What do incoming university students believe about open science practices in

### 2021-05-11 analysis/Manuscript.Rmd
Add degree information

Nearly all reported that they graduated from high
school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
attended high school, a little less than half completed psychology courses in 
high school (*n* = `r hs_psyc[2,2]`). In terms of their nationality, most 
participants reported that they were Australian (*n* = `r nationality[3,2]`), 
from the United Kingdom (*n* = `r nationality[24,2]`), or Chinese 
(*n* = `r nationality[6,2]`). In terms of where the participants were attending 
university, most reported that they were in Australia (*n* = `r uni_country[1,2]`), 
the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). 
Finally, about 2/3rds of participants reported that at least one of their parents 
attended university (*n* = `r first_gen[2,2]`).

@@

```{r include = FALSE}
write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")
crisis_descriptions = read.csv("crisis_descriptions_marked.csv") #categorised as accurate or not
```
Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term. Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Just `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").

>>>>

Nearly all reported that they graduated from high
school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
attended high school, a little less than half completed psychology courses in 
high school (*n* = `r hs_psyc[2,2]`). In terms of their nationality, most 
participants reported that they were Australian (*n* = `r nationality[3,2]`), 
from the United Kingdom (*n* = `r nationality[24,2]`), or Chinese 
(*n* = `r nationality[6,2]`). In terms of where the participants were attending 
university, most reported that they were in Australia (*n* = `r uni_country[1,2]`), 
the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). About 2/3rds of participants reported that at least one of their parents attended university (*n* = `r first_gen[2,2]`). Students were recruited from nine universities, with the largest number of responses recorded from participants enrolled at the University of Queensland (*n* = `r nrow(filter(df, university_recoded == "University of Queensland"))`), University of Adelaide (*n* = `r nrow(filter(df, university_recoded == "University of Adelaide"))`), and the University of Bath (*n* = `r nrow(filter(df, university_recoded == "University of Bath"))`). While, the majority of participants (*n* = `r nrow(filter(df, degree_type == "Non-psychology"))`) indicated that they were enrolled in a non-psychology degree such as a Bachelor of Science or Bachelor of Arts (*n* = `r nrow(filter(df, degree_recoded == "Bachelor of Science"))`, *n* = `r nrow(filter(df, degree_recoded == "Bachelor of Arts"))` respectively), most were completing a psychology major (*n* = `r nrow(filter(df, major_recoded == "Psychology"))`).

@@

```{r include = FALSE, evaluate = FALSE}
write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")
crisis_descriptions = read.csv("crisis_descriptions_marked.csv") #categorised as accurate or not
```
Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term. Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Just `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
